---
title: "CRO Data"
author: "mechelle@bvaccel.com / mariel@bvaccel.com"
date: "3/5/2017"
runtime: shiny
---
<!-- RUN -->
<!--
options(shiny.port = 1222)
#setwd("~/Google Drive/Work/Syntax/R/RMarkdown/")
rmarkdown::run("index.Rmd")
-->

```{r pagination, echo=FALSE}
renderUI({
  req(render3())
  tagList(
    tags$div(class="floating-pagination",
             
             h3("Navigation"),
             a(href="#description", "Report Description"),
             br(),
             a(href="#generate", "Generate a Report"),
             br(),
             a(href="#accountinfo", "Account Information"),
             br(),
             h3("Reports & Graphs"),
             a(href="#dayofweek", "Day of Week"),
              br(),
             a(href="#hourofday", "Hour of Day"),
             br(),
             a(href="#devices", "Devices"),
             br(),
             a(href="#usertype", "New vs Returning"),
             br(),
             a(href="#sourcemedium", "Source / Medium"),
             br(),
             a(href="#landingpage", "Landing Page"),
             br(),
             br(),
             strong(a(href="#", "Return to Top"))
             )
  )
})
```

```{r options & libraries, include=FALSE}
print('test')
options("googleAuthR.webapp.client_id" = "472746344232-0vo77fupf9onf0bs3brrk2jc86b4vlj1.apps.googleusercontent.com")
options("googleAuthR.webapp.client_secret" = "u3EHSLSlUU-Wb0J4AI5RauV5")
options("googleAuthR.scopes.selected" = c("https://www.googleapis.com/auth/webmasters",
                                          "https://www.googleapis.com/auth/analytics",
                                          "https://www.googleapis.com/auth/tagmanager.readonly",
                                          "https://www.googleapis.com/auth/plus.me"))
options("googleAuthR.httr_oauth_cache" = TRUE)
tags$style(type="text/css",
  ".shiny-output-error { visibility: hidden; }",
  ".shiny-output-error:before { visibility: hidden; }"
)

require('googleAuthR')
require('RGA')
require('d3heatmap')
require('xlsx')
```
```{r authorize, echo=FALSE}
auth <- callModule(gar_auth_js, "auth_demo")
# .onAttach <- function(libname, pkgname){
# 
#   googleAuthR::gar_attach_auto_auth(" https://www.googleapis.com/oauth2/v1/tokeninfo",
#                                     environment_var = "GAR_AUTH_FILE")
# }
# .onAttach(libname = '/usr/local/lib/R/auth', pkgname = 'googleAuthR')
# Sys.getenv()
# GAR_AUTH_FILE='/usr/local/lib/R/auth' 
```
</br>
```{r date & account, echo=FALSE, error=FALSE}

vals <- reactiveValues(account = NULL)
valsReact <- reactiveValues(id = NULL)

# capture profiles
prof <- reactive({
  req(auth())
  authorize(token=auth())
  vals$account <- list_accounts()
  selectInput("account", 
    "Choose Account:", 
  vals$account$name, selectize = TRUE)
})

render2 <- reactive({
  req(prof())
  # store selected account id
  # if vals account values name is equal to selected account, get selected account id
  valsReact$id <- vals$account[vals$account$name == input$account,]$id 
  # store selected property data
  vals$property <- list_webproperties(accountId = valsReact$id) 
  selectInput("property", 
              "Choose Property:", 
              paste0(vals$property$name,sep = " ", vals$property$id))
})

render3 <- reactive({
  req(render2())
  valsReact$uaid <- vals$property[paste0(vals$property$name,sep = " ", vals$property$id) == input$property,]$id # store selected property id
  vals$view <- list_profiles(accountId = valsReact$id, webPropertyId = valsReact$uaid) # store selected view data
  selectInput("view", 
              "Choose View:", 
              vals$view$name)
  })

dateRange <- reactive({
  req(auth())
  dateRangeInput('dateRange',
      label = 'Date range input: yyyy-mm-dd',
      start = Sys.Date() - 2, end = Sys.Date() + 2
    )
})
```
<section class="wrapper">
<!-- <div class="floating-pagination"> -->
<!-- <a href="#dayofweek">Day of Week</a> -->
<!-- </div> -->

```{r info, echo=FALSE}
tags$h2("Report Description", class="description",
         br())
tags$p("This report pulls data specifically for CRO analysis. All data is collected from Google Analytics and can be exported into an XLSX workbook.",
       br(),
       br(),
       "For comments, questions and bugs please fill out our ",a(href="https://goo.gl/forms/lCxttDAJAmo8Jnbm1", "Google Form.", target="_blank"),
       br(),
       br(),
       "Changelog for current features and upcoming configurations can be viewed ",a(href="https://github.com/TechnicalWebAnalytics/shiny-server/blob/master/bvaccel-datatools/changelog.txt", "here.", target="_blank"),
       br(),
       br(),
       "You can use the pagination to the right to navigate to the available report graphs ( after authorization ).",
       br(),
       br()
       )
```

```{r, echo=FALSE}
tags$h2("Generate a Report", class="generate",
         br())
tags$p("Follow the steps to generate a report.",
       br(),
       br())
tags$h4(em("1. Authorize Google Analytics. Note that if you refresh you will have to reauthorize. We are working on this."))
gar_auth_jsUI("auth_demo", login_text = "Authorize Google")
tags$br()
tags$br()
tags$h4(em("2. Wait for account details to load. This could take a while. If you update any account details please wait for tables and graphs to load. ( We will be installing a progress loader at some point )"))
```
</br>
```{r date, echo=FALSE}
renderUI({
  req(auth())
  tagList(
  tags$h4(em("3. Choose your date range.")),
  dateRange())
})
tags$br()
```
<section class="account-details">
<div class="column1">
```{r, echo=FALSE, error=FALSE}
renderUI({
  req(auth())
  tagList(tags$h4(em("4. Choose your GA details. Once you are in the selection you can hit backspace to search.")),
  prof())
})
```
</div>
<div class="column2">
```{r, echo=FALSE, error=FALSE}
renderUI({
  req(prof())
  render2()
})
```
</div>
<div class="column3">
```{r, echo=FALSE, error=FALSE}
renderUI({
  req(render2())
  render3()
})
```
</div>
```{r download, echo=FALSE}
tags$br()
export <- reactive({
  req(render3())
  downloadButton(outputId = 'export', label = "Magic Button")
})

renderUI({
  req(render3())
  tags$h4(em("5. Export your data ( Currently as an XLSX ). Or you can view the data in the graphs below."))
})

renderUI({
  req(render3())
  downloadButton("downloadData", "The Magic Button")})

reactive({
  req(render3())
  client <- data.frame(t(clientdata$data))
  dow <- data.frame(values$DayOfWeek)
  hod <- values$HourOfDay
  dev <- values$Devices
  ut <- values$UserType
  sm <- values$SourceMedium
  lp <- values$LandingPage

  output$downloadData <- downloadHandler(
    filename = function() {
      paste("crodata-", Sys.Date(), ".xlsx", sep="")
    },
    content = function(file) {
        write.xlsx(dow, file, sheetName = 'RAW Day of Week')
        write.xlsx(hod, file, append=TRUE, sheetName = 'RAW Hour of Day')
        write.xlsx(dev, file, append=TRUE, sheetName = 'RAW Devices')
        write.xlsx(ut, file, append=TRUE, sheetName = 'RAW New vs Returning')
        write.xlsx(sm, file, append=TRUE, sheetName = 'RAW Source Medium')
        write.xlsx(lp, file, append=TRUE, sheetName = 'RAW Landing Page')

    }
  )})


```
</br>
</section>
```{r, echo=FALSE}
clientdata <- reactiveValues()
client <- reactive({
  req(render3())
  v <- vals$view[vals$view$name == input$view,]$id
  
  property <- data.frame(as.matrix(get_webproperty(valsReact$id,valsReact$uaid)))
  view <- data.frame(get_profile(accountId = valsReact$id,webPropertyId = valsReact$uaid,profileId = v))
  createdDate <- view$created[1]
  permissions <- data.frame(view$effective)
  plength <- nrow(permissions)
  
  x <- data.frame(
    Name             = property['name',],
    WebsiteURL       = view$websiteUrl[1],
    Industy          = property['industryVertical',],
    Currency         = view$currency[1],
    Timezone         = view$timezone[1],
    Permissions      = paste(permissions[1:plength,],collapse=", "),
    AccountID        = property['accountId',],
    UAID             = property['id',],
    ViewID           = view$id[1],
    Created          = createdDate,
    stringsAsFactors = FALSE
    )
  
  clientdata$data <- x
})

renderUI({
  req(client())
tags$h2("Account Information", class="accountinfo",
         br())
})

renderUI({
  req(client())
  tagList(div(class='infocolumn1',
    br(),
    h4(strong("Name")),
    h4(clientdata$data$name),
     br(),
     br(),
    h4(strong("URL")),
    h4(clientdata$data$WebsiteURL),
     br(),
     br(),
    h4(strong("Industry")),
    h4(clientdata$data$industryVertical),
     br(),
     br(),
    h4(strong("Currency")),
    h4(clientdata$data$Currency),
     br(),
     br(),
    h4(strong("Timezone")),
    h4(clientdata$data$Timezone),
     br(),
     br()
  ),
  div(class='infocolumn2',
    br(),
    h4(strong("Permissions")),
    h4(clientdata$data$Permissions),
     br(),
     br(),
    h4(strong("Account ID")),
    h4(clientdata$data$accountId),
     br(),
     br(),
    h4(strong("UAID")),
    h4(clientdata$data$id),
     br(),
     br(),
    h4(strong("View ID")),
    h4(clientdata$data$ViewID),
     br(),
     br(),
    h4(strong("Created")),
    h4(clientdata$data$Created),
    br()
  )
  )
  })

```

<div class="graphs">
```{r, echo=FALSE}
renderUI({
  req(render3())
tagList(
h2("Report Graphs & Tables",
         br()
         ),
p('Note: The heatmap is interactive. You can click and drag different sections of the graph to focus on a certain area. Click off the graph to reset'),
br()
)
})

renderUI({
  req(render3())
  tags$h3("Day of the Week", id="dayofweek",
          br(),
          br())
})
renderDataTable({
  req(render3())
  values$DayOfWeek})

renderD3heatmap({d3heatmap(data.matrix(values$dayofweekheatmap), scale = "column", colors = "Blues", dendrogram = "none", xaxis_font_size = "11px", yaxis_font_size = "11px", Rowv=FALSE, Colv=FALSE, column_names_max_height = TRUE)})
```
</br>
```{r, echo=FALSE}
renderUI({
  req(render3())
  tags$h3("Hour of Day", id="hourofday",
          br(),
          br())
})
renderDataTable({
  req(render3())
  values$HourOfDay})

renderD3heatmap({d3heatmap(data.matrix(values$HourOfDayheatmap), scale = "column", colors = "Blues", dendrogram = "none", xaxis_font_size = "11px", yaxis_font_size = "11px", Rowv=FALSE, Colv=FALSE, column_names_max_height = TRUE)})
```

```{r, echo=FALSE}
renderUI({
  req(render3())
  tags$h3("Devices", id="devices",
          br(),
          br())
})
renderDataTable({
  req(render3())
  values$Devices})

renderD3heatmap({d3heatmap(data.matrix(values$Devicesheatmap), scale = "column", colors = "Blues", dendrogram = "none", xaxis_font_size = "11px", yaxis_font_size = "11px", Rowv=FALSE, Colv=FALSE, column_names_max_height = TRUE)})
```

```{r, echo=FALSE}
renderUI({
  req(render3())
  tags$h3("New vs Returning", id="usertype",
          br(),
          br())
})
renderDataTable({
  req(render3())
  values$UserType})

renderD3heatmap({d3heatmap(data.matrix(values$UserTypeheatmap), scale = "column", colors = "Blues", dendrogram = "none", xaxis_font_size = "11px", yaxis_font_size = "11px", Rowv=FALSE, Colv=FALSE, column_names_max_height = TRUE)})
```

```{r, echo=FALSE}
renderUI({
  req(render3())
  tags$h3("Source / Medium", id="sourcemedium",
          br(),
          br())
})
renderDataTable({
  req(render3())
  values$SourceMedium})

renderD3heatmap({d3heatmap(data.matrix(values$SourceMediumheatmap), scale = "column", colors = "Blues", dendrogram = "none", xaxis_font_size = "11px", yaxis_font_size = "11px", Rowv=FALSE, Colv=FALSE, column_names_max_height = TRUE)})
```

```{r, echo=FALSE}
renderUI({
  req(render3())
  tags$h3("Landing Page", id="landingpage",
          br(),
          br())
})
renderDataTable({
  req(render3())
  values$LandingPage})

renderD3heatmap({d3heatmap(data.matrix(values$LandingPageheatmap), scale = "column", colors = "Blues", dendrogram = "none", xaxis_font_size = "11px", yaxis_font_size = "11px", Rowv=FALSE, Colv=FALSE, column_names_max_height = TRUE)})
```
</div>
</section>
<section class="sub-pages">
<!-- <br></br> -->
<!-- <input type="button" name="test-page1" value="Page1" class="button"> -->
<br></br>
</section>
</div>
```{r, echo=FALSE}
values <- reactiveValues()

reactive({
req(render3())
startDate <- as.Date(input$dateRange[1])
endDate <- as.Date(input$dateRange[2])
# Day of Week Performance
# - Conversion Rate

view <- vals$view[vals$view$name == input$view,]$id

#-------------| Day of Week |---------------#

DayOfWeek <- get_ga(view,
  start.date = startDate,
  end.date   = endDate,
  metrics    = "
  ga:sessions,
  ga:pageviews,
  ga:newUsers,
  ga:bounceRate,
  ga:avgPageLoadTime,
  ga:transactions,
  ga:transactionRevenue,
  ga:revenuePerTransaction,
  ga:transactionsPerSession",
  dimensions = "ga:dayOfWeek",
  sort       = "ga:dayOfWeek",
  # fetch.by = "week"
  )

DayOfWeek[1,1] <- "Sunday"
DayOfWeek[2,1] <- "Monday"
DayOfWeek[3,1] <- "Tuesday"
DayOfWeek[4,1] <- "Wednesday"
DayOfWeek[5,1] <- "Thursday"
DayOfWeek[6,1] <- "Friday"
DayOfWeek[7,1] <- "Caturday"

colnames(DayOfWeek) <- c('Day of Week',
 'Sessions',
 'Pageviews',
 'NewUsers',
 'Bounce Rate',
 'Site Speed',
 'Transactions',
 'Revenue',
 'AOV',
 'CNV'
 )

DayOfWeek$`Bounce Rate` <- as.numeric(DayOfWeek$`Bounce Rate`)/100
DayOfWeek$`CNV` <- as.numeric(DayOfWeek$`CNV`)/100
values$DayOfWeek <- DayOfWeek

heatmap <- DayOfWeek
rownames(heatmap) <- heatmap[,1]
heatmap[,1] <- NULL
values$dayofweekheatmap <- heatmap

#-------------| Devices |---------------#

# Device
# - Sessions
# - Conversion Rate
# - Revenue
# - Transactions

Devices <- get_ga(view,
  start.date = startDate,
  end.date   = endDate,
  metrics    = "
  ga:sessions,
  ga:pageviews,
  ga:newUsers,
  ga:bounceRate,
  ga:avgPageLoadTime,
  ga:transactions,
  ga:transactionRevenue,
  ga:revenuePerTransaction,
  ga:transactionsPerSession",
  dimensions = "ga:deviceCategory",
  sort       = "-ga:sessions"
  # fetch.by = "week",
  )

colnames(Devices) <- c('Device',
 'Sessions',
 'Pageviews',
 'NewUsers',
 'Bounce Rate',
 'Site Speed',
 'Transactions',
 'Revenue',
 'Avg Order Value',
 'Conversion Rate'
 )

Devices$`Bounce Rate` <- as.numeric(Devices$`Bounce Rate`)/100
Devices$`Conversion Rate` <- as.numeric(Devices$`Conversion Rate`)/100
values$Devices <- Devices

heatmap <- Devices
rownames(heatmap) <- heatmap[,1]
heatmap[,1] <- NULL
values$Devicesheatmap <- heatmap

#-------------| Hour of Day |---------------#
# Hour of Day
# - Conversion Rate

HourOfDay <- get_ga(view,
  start.date = startDate,
  end.date   = endDate,
  metrics    = "
  ga:sessions,
  ga:pageviews,
  ga:newUsers,
  ga:bounceRate,
  ga:avgPageLoadTime,
  ga:transactions,
  ga:transactionRevenue,
  ga:revenuePerTransaction,
  ga:transactionsPerSession",
  dimensions = "ga:hour",
  sort       = "ga:hour"
  # fetch.by = "week",
  )

colnames(HourOfDay) <- c('Hour of Day',
 'Sessions',
 'Pageviews',
 'NewUsers',
 'Bounce Rate',
 'Site Speed',
 'Transactions',
 'Revenue',
 'Avg Order Value',
 'Conversion Rate'
 )

HourOfDay$`Bounce Rate` <- as.numeric(HourOfDay$`Bounce Rate`)/100
HourOfDay$`Conversion Rate` <- as.numeric(HourOfDay$`Conversion Rate`)/100
values$HourOfDay <- HourOfDay

heatmap <- HourOfDay
rownames(heatmap) <- heatmap[,1]
heatmap[,1] <- NULL
values$HourOfDayheatmap <- heatmap

#-------------| New v Returning |---------------#
# New v Returning
# - Conversion Rate
# - Revenue

UserType <- get_ga(view,
  start.date = startDate,
  end.date   = endDate,
  metrics    = "
  ga:sessions,
  ga:pageviews,
  ga:newUsers,
  ga:bounceRate,
  ga:avgPageLoadTime,
  ga:transactions,
  ga:transactionRevenue,
  ga:revenuePerTransaction,
  ga:transactionsPerSession",
  dimensions = "ga:userType",
  sort       = "-ga:sessions"
  # fetch.by = "week",
  )

colnames(UserType) <- c('User Type',
 'Sessions',
 'Pageviews',
 'NewUsers',
 'Bounce Rate',
 'Site Speed',
 'Transactions',
 'Revenue',
 'Avg Order Value',
 'Conversion Rate'
 )

UserType$`Bounce Rate` <- as.numeric(UserType$`Bounce Rate`)/100
UserType$`Conversion Rate` <- as.numeric(UserType$`Conversion Rate`)/100
values$UserType <- UserType

heatmap <- UserType
rownames(heatmap) <- heatmap[,1]
heatmap[,1] <- NULL
values$UserTypeheatmap <- heatmap

#-------------| Source / Medium |---------------#
# Source / Medium
# - Sessions
# - Conversion Rate
# - Revenue

SourceMedium <- get_ga(view,
  start.date = startDate,
  end.date   = endDate,
  metrics    = "
  ga:sessions,
  ga:pageviews,
  ga:newUsers,
  ga:bounceRate,
  ga:avgPageLoadTime,
  ga:transactions,
  ga:transactionRevenue,
  ga:revenuePerTransaction,
  ga:transactionsPerSession",
  dimensions = "ga:sourceMedium",
  sort       = "-ga:sessions"
  # fetch.by = "week",
  )

colnames(SourceMedium) <- c('Source / Medium',
 'Sessions',
 'Pageviews',
 'NewUsers',
 'Bounce Rate',
 'Site Speed',
 'Transactions',
 'Revenue',
 'Avg Order Value',
 'Conversion Rate'
 )

SourceMedium$`Bounce Rate` <- as.numeric(SourceMedium$`Bounce Rate`)/100
SourceMedium$`Conversion Rate` <- as.numeric(SourceMedium$`Conversion Rate`)/100
values$SourceMedium <- SourceMedium

heatmap <- SourceMedium
rownames(heatmap) <- heatmap[,1]
heatmap[,1] <- NULL
values$SourceMediumheatmap <-  head(heatmap, n=25)

#-------------| Landing Pages |---------------#
# Landing Pages
# - New Users
# - Bounce Rate
# - Conversion Rate
# - Revenue

LandingPage <- get_ga(view,
  start.date = startDate,
  end.date   = endDate,
  metrics    = "
  ga:sessions,
  ga:pageviews,
  ga:newUsers,
  ga:bounceRate,
  ga:avgPageLoadTime,
  ga:transactions,
  ga:transactionRevenue,
  ga:revenuePerTransaction,
  ga:transactionsPerSession",
  dimensions = "ga:landingPagePath",
  sort       = "-ga:sessions"
  # fetch.by = "week",
  )

colnames(LandingPage) <- c('Landing Page',
 'Sessions',
 'Pageviews',
 'NewUsers',
 'Bounce Rate',
 'Site Speed',
 'Transactions',
 'Revenue',
 'Avg Order Value',
 'Conversion Rate'
 )

LandingPage$`Bounce Rate` <- as.numeric(LandingPage$`Bounce Rate`)/100
LandingPage$`Conversion Rate` <- as.numeric(LandingPage$`Conversion Rate`)/100
values$LandingPage <- LandingPage

heatmap <- LandingPage
rownames(heatmap) <- heatmap[,1]
heatmap[,1] <- NULL
values$LandingPageheatmap <- head(heatmap, n=25)
})
```

<style type="text/css">
.container-fluid.main-container {
  width: 100%;
  max-width: 100%;
  margin-left: 1%;
  margin-right: 1%;
}

.floating-pagination {
    position: fixed;
    right: 1%;
    top: 1.5%;
    padding: 0 15px 10px 15px;
    background-color: rgba(158, 158, 158, 0.21);
    z-index: 9999;
    border-radius: 5px;
}

.account-details {
  width: 60%;
}

.column1 {
/*float: left;*/
/*width: 30%;*/
margin-right: 2%;
}

.column2 {
/*float: left;*/
/*width: 30%;*/
margin-right: 2%;
}

.column3 {
/*float: left;*/
/*width: 30%;*/
margin-right: 2%;
}

.sub-pages {
clear: both;
}

.wrapper {
width: 90%;
}

.infocolumn1 {
float: left;
width: 20%;
}

.graphs {
margin-right: 4%;
clear: both;
}

.shiny-output-error {
visibility:hidden;
}

</style>

<script>
$(".sub-pages").click(function(){
  $(".graphs").show();
});
</script>